---
title: "Syllabus Electiva I: Globalización Económica Module A AE"
author: "Distance Learning Faculty (FAEDIS)"
date: "2022-1"
output:
  pdf_document:
    number_sections: yes
  html_document:
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 4
bibliography: econ_glob_faedis.bib
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
```

```{r}

library(tidyverse)
library(knitr)
```

# Professor and meeting hours with students

- __Name__

    + Luis Francisco Gomez Lopez

- __Communication through the virtual classroom__

    + Every Saturday between 07:00 hours and 08:00 hours: 
    
        + _Primer Corte 30% > Virtual Meetings > Meeting hours with students_
    
    + Doubts and concerns of the topics of the course, please use the _Forum: Questions or concerns_ that can be accessed at the top of the platform
    
        + In this way, doubts can be shared with all students and all course participants can contribute to the learning process
    
    + Complaints regarding grades, please send an email to __luis.gomezl@unimilitar.edu.co__
    
        + To make any complaints, you are asked to wait first for the grades to be published on the News Bulletin Board and to be made based on the feedbacks that will be made taking into account the evaluation parameters
        
        + Urgent issues, you can call me to +57 3124541536 Tuesday, Thursday and Friday between 14:30 hours and 15:30 hours. Please do not send me whatsapp messages or call me on weekends.

# Presentation and objectives of the subject

## Description

- Credits: 4
- Type: Theoretical-Practice
- Area of Knowledge: Professional
- Semester: 8
- Block: 1 (January 24 – March 27, 2022) 

## Justification

In a globalized world, the future business manager requires to understand the dynamics of globalization processes. In that way, he can detect new opportunities that allow organizations to be able to benefit from international trade and economic integration.
 
 One of the aspects that has the greatest importance for the skills of the future business manager is economics and its relationship with aspects of international business management. In that sense, future professionals require a series of theoretical and practical tools to define corporate strategies as well as to manage operations within the international sphere to make better decisions in an uncertain environment.
 
 Consequently, the basic knowledge of economic theory and its relationship with business management is essential to define and plan actions related to the international economic macro-environment in which an organization operates.

## General objective

Familiarize students with the international economic macro-environment in which businesses develop, their main variables, opportunities, and threats within the context of globalization and specifically concerning the processes of economic integration.

# Competencies

- Global competency:

    + Define and plan actions based on information from the international economic macro-environment in which an organization performs to achieve strategic organizational objectives.

- Specific competencies:

    + Formulate management plans based on the organizational structure and the international economic macro-environment to benefit the organization and its local environment
    
    + Manage financial resources based on information from the organization and the international economic macro-environment to achieve strategic organizational objectives
    
    + Manage international operations related to global manufacturing and supply chain to achieve strategic organizational objectives

- Competencies SABE curriculum

    + Skills in handling a second language
    + Ability to work in teams
    + Ability to use the scientific method and logical thinking
    + Ability to assess the ethical, moral and conflict of interest implications in the professional practice
    
# Schedule and contents

## Reading schedule

```{r}

tibble(Week = c(1:9),
       Material       = rep("[@wild_international_2020]", times = 9),
       Chapter        = c(1, 5, 8, 9, 10, 12, 13, 15, 3),
       `Initial page` = c(28, 154, 222, 246, 270, 316, 340, 386, 96),
       `Final page`   = c(65, 177, 245, 269, 293, 339, 365, 405, 127)) %>%
    mutate(`Number of pages` = (`Final page` - `Initial page`) + 1) %>% 
    kable()
```

## Detailed schedule of virtual meetings and activities

### Primer corte 30%

- January 24

    + Start Block 1

    + __Virtual meeting Presentation Syllabus__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:
            + Review the course program in advance, which can be downloaded by following the route _Primer corte 30% > Learning Resources > Support material > Presentations > 000_syllabus_econ_glob_2022_1_
            + Have a headset with a built-in microphone to isolate noise from the environment
            
- January 27

    + __Virtual meeting Global business environment__
        + __Meeting time__: 19:00 - 19:45 hours 
        + __Prerequisites__: 
            + Read and review [@wild_international_2020, Chapter 1]
            + Have a headset with a built-in microphone to isolate noise from the environment

- January 31

    + __Questionare 1 Opening__
        + __Opening time__: 00:00 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapters 1 & 5]

- February 3

    + __Virtual meeting International trade and investment__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:  
            + Read and review [@wild_international_2020, Chapter 5]
            + Have a headset with a built-in microphone to isolate noise from the environment
            
- February 7

    + __Questionare 1 Closing__
        + __Closing time__: 22:00 hours
        + __Prerequisites__: 
            + Have answered the Questionare 1 before 22:00 hours
            
- February 10

    + __Virtual meeting Regional economic integration__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__: 
            + Read and review [@wild_international_2020, Chapter 8]
            + Have a headset with a built-in microphone to isolate noise from the environment
            
- February 12

    + __Oral presentation Midterm Exam 1 Opening__
        + __Opening time__: 15:30 hours
        + __Closing time__: 17:30 hours
        + __Prerequisites__: 
            + Read and review [@wild_international_2020, Chapter 8]
            + Have a headset with a built-in microphone to isolate noise from the environment

### Segundo corte 30%

- February 14

    + __Questionare 2 Opening__
        + __Opening time__: 00:00 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapters 9 & 10]
        
- February 17

    + __Virtual meeting International financial markets__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapter 9]
            + Have a headset with a built-in microphone to isolate noise from the environment

- February 24

    + __Virtual meeting International monetary system__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapter 10]
            + Have a headset with a built-in microphone to isolate noise from the environment

- February 27

    + __Questionare 2 Closing__
        + __Closing time__: 22:00 hours
        + __Prerequisites__: 
            + Have answered the Questionare 2 before 22:00 hours

- March 3

    + __Virtual meeting Analyzing international opportunities__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapter 12]
            + Have a headset with a built-in microphone to isolate noise from the environment

- March 5

    + __Oral presentation Midterm Exam 2 Opening__
        + __Opening time__: 15:30 hours
        + __Closing time__: 17:30 hours
        + __Prerequisites__: 
            + Read and review [@wild_international_2020, Chapter 12]
            + Have a headset with a built-in microphone to isolate noise from the environment

### Tercer corte 40%

- March 7

    + __Questionare 3 Opening__
        + __Opening time__: 00:00 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapters 13 & 15]

- March 10

    + __Virtual meeting Selecting and managing entry modes__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapter 13]
            + Have a headset with a built-in microphone to isolate noise from the environment

- March 17

    + __Virtual meeting Managing international operations__
        + __Meeting time__: 19:00 - 19:45 hours
        + __Prerequisites__:
            + Read and review [@wild_international_2020, Chapter 15]
            + Have a headset with a built-in microphone to isolate noise from the environment
            
- March 20

    + __Questionare 3 Closing__
        + __Closing time__: 22:00 hours
        + __Prerequisites__: 
            + Have answered the Questionare 3 before 22:00 hours

- March 24
    
    + __Virtual meeting Political economy and ethics__
        + __Opening time__: 19:00 - 19:45 hours
        + Prerequisites:
            + Read and review [@wild_international_2020, Chapter 3]
            + Have a headset with a built-in microphone to isolate noise from the environment

- March 26
            
    + __Oral presentation Final Exam Opening__
        + __Opening time__: 15:30 hours
        + __Closing time__: 17:30 hours
        + __Prerequisites__: 
            + Read and review [@wild_international_2020, Chapter 3]
            + Have a headset with a built-in microphone to isolate noise from the environment
            
# Qualifiable activities, weights and process in case of no presentation

## Activities and weights

- __Primer corte__: 30%

    + __Questionare 1__: 15% 
    + __Oral presentation Midterm Exam 1__: 15% 

- __Segundo corte__: 30%

    + __Questionare 2__: 15% 
    + __Oral presentation Midterm Exam 2__: 15%

- __Tercer corte__: 40%

    + __Questionare 3__: 15%
    + __Oral presentation Final Exam__: 25 %
    
## Process in case of no presentation

- Students who do not present a __Questionare__ due to force majeure or illness, must send the respective excuse scanned through the __luis.gomezl@unimilitar.edu.co__. If it is not sent, the note will be zero. Once the excuse has been satisfactorily received, the student should __not__ present the activity and the corresponding grade will be equal to the immediately subsequent grade obtained in the __Midterm Exam 1__ or __Midterm Exam 2__ or __Final Exam__ according to the case.

- Students who do not present a __Midterm Exam 1__ or __Midterm Exam 2__ or the __Final Exam__, must send and email to _admon.distancia@unimilitar.edu.co_ two days before or two days after the closing date of these activities. However, this request can be made only once during the course. If it is not requested under these conditions, the grade will be zero.

# Study material

- [@wild_international_2020, Chapters 1, 3, 5, 8, 9, 10, 12, 13 & 15]

    + The book can be consulted through the route _http://www.ebooks7-24.com.ezproxy.umng.edu.co/?il=8857 > Login with username and password_ [^1]

[^1]: Remember that the user and password to access and read the e-book are the same that you use to check your grades

# About plagiarism

- __Acuerdo 02 de 2015 (7 de Mayo): Artículo 68. Escala de Calificaciones Numeral f__ 

_"La comprobación de todo fraude o intento de fraude en cualquier tipo de prueba, acarreará al estudiante y a su(s) colaborador(es), una calificación de CERO PUNTO CERO (0.0) en la prueba respectiva. Como quiera que el fraude o intento de cometerlo es una falta grave, el docente debe informar de este hecho al Director del programa respectivo, quien enviará el informe a la Decanatura de la Facultad, con el fin de iniciar los trámites correspondientes para aplicar la sanción disciplinaria prevista en éste reglamento.”_

- __Acuerdo 05 de 2018 (6 de Junio): Artículo 20 que modifica el Artículo 107 Faltas Disciplinarias Numeral c. Número 6 del Acuerdo 02 de 2015 (7 de Mayo)__

_"Hacer plagio en cualquier tipo de documento o desplegar alguna conducta dolosa que viole el régimen de propiedad intelectual de la Universidad."_

# Study material references
