---
title: 'Syllabus Electiva I: Globalización Económica Module A AE'
author: Distance Learning Faculty (FAEDIS)
date: '2023-07'
format:
  pdf: 
    number-sections: true
    number-depth: 4
    urlcolor: blue
    colorlinks: true
    link-citations: true
    linkcolor: blue
bibliography: econ_glob_faedis.bib
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
```

```{r}
library(tidyverse)
library(knitr)
```

# Professor and meeting hours with students

-   **Name**

    -   Luis Francisco Gomez Lopez

-   **Communication through the virtual classroom**

    -   Every Saturday between 07:00 hours and 08:00 hours:

        -   *Primer Corte 30% \> Virtual Meetings \> Meeting hours with students*

    -   Doubts and concerns of the topics of the course, please use the *Forum: Questions or concerns* that can be accessed at the top of the platform

        -   In this way, doubts can be shared with all students and all course participants can contribute to the learning process

    -   Complaints regarding grades, please send an email to [**luis.gomezl\@unimilitar.edu.co**](mailto:luis.gomezl@unimilitar.edu.co){.email}

        -   To make any complaints, you are asked to wait first for the grades to be published on the News Bulletin Board and to be made based on the feedbacks that will be made taking into account the evaluation parameters

        -   Urgent issues, you can call me to +57 3124541536 Tuesday, Thursday and Friday between 14:30 hours and 15:30 hours. Please do not send me whatsapp messages or call me on weekends.

# Presentation and objectives of the subject

## Description

-   Credits: 4
-   Type: Theoretical-Practice
-   Area of Knowledge: Professional
-   Semester: 8
-   Block: 1 (July 24 -- September 24, 2023)

## Justification

In a globalized world, the future business manager requires to understand the dynamics of globalization processes. In that way, he can detect new opportunities that allow organizations to be able to benefit from international trade and economic integration.

One of the aspects that has the greatest importance for the skills of the future business manager is economics and its relationship with aspects of international business management. In that sense, future professionals require a series of theoretical and practical tools to define corporate strategies as well as to manage operations within the international sphere to make better decisions in an uncertain environment.

Consequently, the basic knowledge of economic theory and its relationship with business management is essential to define and plan actions related to the international economic macro-environment in which an organization operates.

## General objective

Familiarize students with the international economic macro-environment in which businesses develop, their main variables, opportunities, and threats within the context of globalization and specifically concerning the processes of economic integration.

# Competencies

-   Global competency:

    -   Define and plan actions based on information from the international economic macro-environment in which an organization performs to achieve strategic organizational objectives.

-   Specific competencies:

    -   Formulate management plans based on the organizational structure and the international economic macro-environment to benefit the organization and its local environment

    -   Manage financial resources based on information from the organization and the international economic macro-environment to achieve strategic organizational objectives

    -   Manage international operations related to global manufacturing and supply chain to achieve strategic organizational objectives

-   Competencies SABE curriculum

    -   Skills in handling a second language
    -   Ability to work in teams
    -   Ability to use the scientific method and logical thinking
    -   Ability to assess the ethical, moral and conflict of interest implications in the professional practice

# Schedule and contents

## Reading schedule

```{r}

tibble(Week = c(1:9),
       Material       = rep("[@wild_international_2020]", times = 9),
       Chapter        = c(1, 5, 8, 9, 10, 12, 13, 15, 3),
       `Initial page` = c(28, 154, 222, 246, 270, 316, 340, 386, 96),
       `Final page`   = c(65, 177, 245, 269, 293, 339, 365, 405, 127)) %>%
    mutate(`Number of pages` = (`Final page` - `Initial page`) + 1) %>% 
    kable()
```

## Detailed schedule of virtual meetings and activities

### Primer corte 30%

-   July 24

    -   Start Block 1

    -   **Virtual meeting Presentation Syllabus**

        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Review the course program in advance, which can be downloaded by following the route *Primer corte 30% \> Learning Resources \> Support material \> Presentations \> 000_syllabus_econ_glob_2023_2*
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   July 27

    -   **Virtual meeting Global business environment**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 1]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   July 31

    -   **Questionare 1 Opening**
        -   **Opening time**: 00:00 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapters 1, 5]

-   August 3

    -   **Virtual meeting International trade theory**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 5]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   August 6

    -   **Questionare 1 Closing**
        -   **Closing time**: 22:00 hours
        -   **Prerequisites**:
            -   Have answered the Questionare 1 before 22:00 hours

-   August 10

    -   **Virtual meeting Regional economic integration**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 8]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   August 12

    -   **Oral presentation Midterm Exam 1 Opening**
        -   **Opening time**: 15:30 hours
        -   **Closing time**: 17:30 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 8]
            -   Have a headset with a built-in microphone to isolate noise from the environment

### Segundo corte 30%

-   August 14

    -   **Questionare 2 Opening**
        -   **Opening time**: 00:00 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapters 9, 10]

-   August 17

    -   **Virtual meeting International financial markets**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 9]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   August 24

    -   **Virtual meeting International monetary system**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 10]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   August 27

    -   **Questionare 2 Closing**
        -   **Closing time**: 22:00 hours
        -   **Prerequisites**:
            -   Have answered the Questionare 2 before 22:00 hours

-   August 31

    -   **Virtual meeting Analyzing international opportunities**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 12]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   September 2

    -   **Oral presentation Midterm Exam 2 Opening**
        -   **Opening time**: 15:30 hours
        -   **Closing time**: 17:30 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 12]
            -   Have a headset with a built-in microphone to isolate noise from the environment

### Tercer corte 40%

-   September 4

    -   **Questionare 3 Opening**
        -   **Opening time**: 00:00 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapters 13, 15]

-   September 7

    -   **Virtual meeting Selecting and managing entry modes**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 13]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   September 14

    -   **Virtual meeting Managing international operations**
        -   **Meeting time**: 19:00 - 19:45 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 15]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   September 17

    -   **Questionare 3 Closing**
        -   **Closing time**: 22:00 hours
        -   **Prerequisites**:
            -   Have answered the Questionare 3 before 22:00 hours

-   September 21

    -   **Virtual meeting Political economy and ethics**
        -   **Opening time**: 19:00 - 19:45 hours
        -   Prerequisites:
            -   Read and review [@wild_international_2020, Chapter 3]
            -   Have a headset with a built-in microphone to isolate noise from the environment

-   September 23

    -   **Oral presentation Final Exam Opening**
        -   **Opening time**: 15:30 hours
        -   **Closing time**: 17:30 hours
        -   **Prerequisites**:
            -   Read and review [@wild_international_2020, Chapter 3]
            -   Have a headset with a built-in microphone to isolate noise from the environment

# Qualifiable activities, weights and process in case of no presentation

## Activities and weights

-   **Primer corte**: 30%

    -   **Questionare 1**: 15%
    -   **Oral presentation Midterm Exam 1**: 15%

-   **Segundo corte**: 30%

    -   **Questionare 2**: 15%
    -   **Oral presentation Midterm Exam 2**: 15%

-   **Tercer corte**: 40%

    -   **Questionare 3**: 15%
    -   **Oral presentation Final Exam**: 25 %

## Process in case of no presentation

-   Students who do not present a **Questionare** due to force majeure or illness, must send the respective excuse scanned through the [**luis.gomezl\@unimilitar.edu.co**](mailto:luis.gomezl@unimilitar.edu.co){.email}. If it is not sent, the note will be zero. Once the excuse has been satisfactorily received, the student should **not** present the activity and the corresponding grade will be equal to the immediately subsequent grade obtained in the **Midterm Exam 1** or **Midterm Exam 2** or **Final Exam** according to the case.

-   Students who do not present a **Midterm Exam 1** or **Midterm Exam 2** or the **Final Exam**, must send and email to [**admon.distancia\@unimilitar.edu.co**](mailto:admon.distancia@unimilitar.edu.co){.email} two days before or two days after the closing date of these activities. However, this request can be made only once during the course. If it is not requested under these conditions, the grade will be zero.

# Use of Chat GPT-3, PaLM 2 (used in BART) and its friends

You can use any artificial intelligence tool and in particular any Large Language Model but please use them in a responsible way by taking into account its capabilities and limitations and always pointing out to the professor and your colleges that you have use them

# Study material

-   [@wild_international_2020, Chapters 1, 3, 5, 8, 9, 10, 12, 13, 15]

    -   The book can be consulted through the route [*http://www.ebooks7-24.com.ezproxy.umng.edu.co/?il=8857*](http://www.ebooks7-24.com.ezproxy.umng.edu.co/?il=8857) *\> Login with username and password* [^1]

[^1]: Remember that the user and password to access and read the e-book are the same that you use to check your grades

# References
