---
title: "International monetary system"
author: "Luis Francisco Gomez Lopez"
date: 2022-06-10 09:57:44
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme: structurebold
    theme: AnnArbor
    fig_caption: true
  ioslides_presentation: default
  slidy_presentation: default
bibliography: econ_glob_faedis.bib
link-citations: yes
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo      = FALSE, 
                      warning   = FALSE, 
                      message   = FALSE,
                      fig.align = "center")
```

```{r libraries}

library(tidyverse)
library(tidyquant)
library(lubridate)
library(moments)
library(timetk)
```

# Contents

- Please Read Me
- Purpose
- Analysis of exchange rates
- Simple model of exchange rates determination
- Implicit devaluation
- Acknowledgments
- References

# Please Read Me

- Check the message __Welcome greeting__ published in the News Bulletin Board.

- Dear student please edit your profile uploading a photo where your face is clearly visible.

- The purpose of the virtual meetings is to answer questions and not to make a summary of the study material.

- This presentation is based on [@wild_international_2020, Chapter 10]

# Purpose

Analyze the importance of exchange rates to international business management and the factors that determine them

# Analysis of exchange rates

- Knowing the data

    + __Variable__: Market Representative Exchange Rate (MRE)[^1] COP/USD
    
        + Calculation methodology: [@banrep_circular_2018]
        
        + Only includes operations agreed by the Exchange Market Intermediaries (EMI)[^2] with other entities supervised by the Superintendencia Financiera de Colombia (SFC) and with the Nación - Ministerio de Hacienda y Crédito Público
        
        + The MRE is calculated and certified daily by the SFC with the operations of the day and will be effective for the next day

[^1]: Tasa de Cambio Representativa del Mercado (TRM) in spanish
[^2]: Intermediarios del Mercado Cambiario (IMC) in spanish
        
# Analysis of exchange rates

- Knowing the data

    + __Variable__: Market Representative Exchange Rate (MRE) COP/USD
    
        + The MRE in a business day following a holiday of the Federal Reserve banks of the United States of America will be the same MRE in effect on the holiday
        
        + For saturdays, sundays, holidays and those in which the Banco de la República does not provide the services of the "Sistema de Cuentas de Depósito", the MRE in force on the immediately following business day will apply
        
    + __Data source__: https://www.banrep.gov.co/ > Estadísticas > ¡NUEVO! Estadísticas Banrep >  CATÁLOGO DE SERIES > Tasas de cambio y sector externo > Tasas de cambio nominales > Tasa Representativa del Mercado (TRM) > DESCARGAR
    
# Analysis of exchange rates

- Visualizing the data

```{r, out.width="80%"}

# Data
cop_usd_trm <- read_csv(file   = "005_trm_cop_usd_consolidado_series.csv") %>% 
  set_names(nm = c("date", "trm")) %>% 
  mutate(trm_change = (trm - lag(trm)))

# Plot
cop_usd_trm %>%
  ggplot(aes(x = date, y = trm)) +
  geom_line(color = palette_light()[[1]]) +
  geom_vline(xintercept = ymd("1999-09-25"),
             color      = palette_light()[[3]]) +
  annotate(x     = ymd("1995-01-01"), 
           y     = 3500, 
           geom  = "label",
           color = "white",
           fill  = palette_light()[[1]],
           label = str_glue("On 1999-09-25
                              the currency band system 
                              was abandoned by
                              the Bank of the
                              Republic")) +
  labs(x        = "",
       y        = "COP/USD",
       title    = "Daily MRE (COP/USD)", 
       subtitle = str_glue("Period: {cop_usd_trm$date[1]} - {cop_usd_trm$date[length(cop_usd_trm$date)]},
                             Observations: {length(cop_usd_trm$trm)}"),
       caption  = str_glue("Data source: Banco de la República (Colombia) & Superintendencia Financiera de Colombia (SFC) 
                             Last update: {cop_usd_trm$date[length(cop_usd_trm$date)]}")) +
  theme(panel.border      = element_rect(fill = NA, color = "black"),
        plot.background   = element_rect(fill = "#f3fcfc"),
        panel.background  = element_rect(fill = "#f3f7fc"),
        legend.background = element_rect(fill = "#f3fcfc"),
        plot.title        = element_text(face = "bold"),
        axis.title        = element_text(face = "bold"),
        legend.title      = element_text(face = "bold"),
        axis.text         = element_text(face = "bold"))
```

# Analysis of exchange rates

- Visualizing the data

```{r, out.width="80%"}

    # Plot
bins <- 30

    # Plot
cop_usd_trm %>% 
    ggplot() + 
    geom_histogram(aes(x = trm),
                   bins = bins + 1, 
                   color = "black", 
                   fill  = palette_light()[[1]],
                   alpha = 0.8, 
                   boundary = min(cop_usd_trm$trm)) +
    scale_x_continuous(labels = scales::number_format(accuracy = 0.01),
                       breaks = seq(from = min(cop_usd_trm$trm),
                                    to   = max(cop_usd_trm$trm), 
                                    by = (max(cop_usd_trm$trm) - min(cop_usd_trm$trm)) / bins)) +
    labs(x        = "",
         y        = "",
         title    = "Frequency distribution: daily MRE (COP/USD)", 
         subtitle = str_glue("Period: {cop_usd_trm$date[1]} - {cop_usd_trm$date[length(cop_usd_trm$date)]}
                             Bins: {bins},
                             Observations: {length(cop_usd_trm$trm)}"),
         caption  = str_glue("Data source: Banco de la República (Colombia) & Superintendencia Financiera de Colombia (SFC) 
                             Last update: {cop_usd_trm$date[length(cop_usd_trm$date)]}")) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          axis.text.x       = element_text(face = "bold", angle = 90, vjust = 0.5),
          axis.text.y       = element_text(face = "bold"))
```

# Analysis of exchange rates

- Visualizing the data

```{r, out.width="80%"}

    # Plot
cop_usd_trm %>% 
    ggplot() + 
    geom_histogram(aes(x = trm, y = after_stat(density)),
                   bins     = bins + 1, 
                   color    = "black", 
                   fill     = palette_light()[[1]],
                   alpha    = 0.8,
                   boundary = min(cop_usd_trm$trm)) +
    geom_density(aes(x = trm), 
                 color    = palette_light()[[2]],
                 size     = 1,
                 linetype = "longdash") +
    scale_x_continuous(labels = scales::number_format(accuracy = 0.01),
                       breaks = seq(from = min(cop_usd_trm$trm),
                                    to   = max(cop_usd_trm$trm), 
                                    by = (max(cop_usd_trm$trm) - min(cop_usd_trm$trm)) / bins)) +
    labs(x        = "",
         y        = "",
         title    = "Empirical probability density function: daily MRE (COP/USD)", 
         subtitle = str_glue("Period: {cop_usd_trm$date[1]} - {cop_usd_trm$date[length(cop_usd_trm$date)]}
                             Bins: {bins},
                             Observations: {length(cop_usd_trm$trm)}"),
         caption  = str_glue("Data source: Banco de la República (Colombia) & Superintendencia Financiera de Colombia (SFC) 
                             Last update: {cop_usd_trm$date[length(cop_usd_trm$date)]}")) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          axis.text.x       = element_text(face = "bold", angle = 90, vjust = 0.5),
          axis.text.y       = element_text(face = "bold"))
```

# Analysis of exchange rates

- Visualizing the data

```{r, out.width="80%"}

# Plot
cop_usd_trm %>% 
    ggplot() + 
    geom_histogram(aes(x = trm_change),
                   bins = bins + 1, 
                   color = "black", 
                   fill  = palette_light()[[1]],
                   alpha = 0.8, 
                   boundary = min(cop_usd_trm$trm_change, na.rm = TRUE)) +
    scale_x_continuous(labels = scales::number_format(accuracy = 0.01),
                       breaks = seq(from = min(cop_usd_trm$trm_change, na.rm = TRUE),
                                    to   = max(cop_usd_trm$trm_change, na.rm = TRUE), 
                                    by = (max(cop_usd_trm$trm_change, na.rm = TRUE) - min(cop_usd_trm$trm_change, na.rm = TRUE)) / bins)) +
    labs(x        = "",
         y        = "",
         title    = "Frequency distribution: daily change MRE COP/USD", 
         subtitle = str_glue("Period: {cop_usd_trm$date[2]} - {cop_usd_trm$date[length(cop_usd_trm$date)]}
                             Bins: {bins},
                             Observations: {length(cop_usd_trm$trm_change[!is.na(cop_usd_trm$trm_change)])}"),
         caption  = str_glue("Data source: Banco de la República (Colombia) & Superintendencia Financiera de Colombia (SFC) 
                             Last update: {cop_usd_trm$date[length(cop_usd_trm$date)]}")) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          axis.text.x       = element_text(face = "bold", angle = 90, vjust = 0.5),
          axis.text.y       = element_text(face = "bold"))
```

# Analysis of exchange rates

- Visualizing the data

```{r, out.width="80%"}

# Plot
cop_usd_trm %>% 
    ggplot() + 
    geom_histogram(aes(x = trm_change, y = ..density..),
                   bins = bins + 1, 
                   color = "black", 
                   fill  = palette_light()[[1]],
                   alpha = 0.8, 
                   boundary = min(cop_usd_trm$trm_change, na.rm = TRUE)) +
    geom_density(aes(x = trm_change), 
                 color    = palette_light()[[2]],
                 size     = 0.5,
                 linetype = "longdash") +
    scale_x_continuous(labels = scales::number_format(accuracy = 0.01),
                       breaks = seq(from = min(cop_usd_trm$trm_change, na.rm = TRUE),
                                    to   = max(cop_usd_trm$trm_change, na.rm = TRUE), 
                                    by = (max(cop_usd_trm$trm_change, na.rm = TRUE) - min(cop_usd_trm$trm_change, na.rm = TRUE)) / bins)) +
    labs(x        = "",
         y        = "",
         title    = "Empirical probability density function: daily change MRE COP/USD", 
         subtitle = str_glue("Period: {cop_usd_trm$date[2]} - {cop_usd_trm$date[length(cop_usd_trm$date)]}
                             Bins: {bins},
                             Observations: {length(cop_usd_trm$trm_change[!is.na(cop_usd_trm$trm_change)])}"),
         caption  = str_glue("Data source: Banco de la República (Colombia) & Superintendencia Financiera de Colombia (SFC) 
                             Last update: {cop_usd_trm$date[length(cop_usd_trm$date)]}")) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          axis.text.x       = element_text(face = "bold", angle = 90, vjust = 0.5),
          axis.text.y       = element_text(face = "bold"))
```

# Analysis of exchange rates

- Visualizing the data

```{r, out.width="80%"}

# Data
cop_usd_trm_filter <- cop_usd_trm %>%
    filter(trm_change != 0)

    # Plot
cop_usd_trm_filter %>% 
    ggplot() + 
    geom_histogram(aes(x = trm_change, y = ..density..),
                   bins = bins + 1, 
                   color = "black", 
                   fill  = palette_light()[[1]],
                   alpha = 0.8, 
                   boundary = min(cop_usd_trm_filter$trm_change, na.rm = TRUE)) +
    geom_density(aes(x = trm_change), 
                 color    = palette_light()[[2]],
                 size     = 0.5,
                 linetype = "longdash") +
    scale_x_continuous(labels = scales::number_format(accuracy = 0.01),
                       breaks = seq(from = min(cop_usd_trm_filter$trm_change, na.rm = TRUE),
                                    to   = max(cop_usd_trm_filter$trm_change, na.rm = TRUE), 
                                    by = (max(cop_usd_trm_filter$trm_change, na.rm = TRUE) - min(cop_usd_trm_filter$trm_change, na.rm = TRUE)) / bins)) +
    geom_vline(xintercept = mean(cop_usd_trm_filter$trm_change),
               color      = palette_light()[[3]],
               size       = 1) +
    geom_segment(data = tibble(x    = (mean(cop_usd_trm_filter$trm_change) - sd(cop_usd_trm_filter$trm_change)),
                               y    = 0,
                               xend = (mean(cop_usd_trm_filter$trm_change) + sd(cop_usd_trm_filter$trm_change)),
                               yend = 0),
                 aes(x = x, y = y, xend = xend, yend = yend),
                 color   = palette_light()[[10]],
                 size    = 1) + 
    labs(x        = "",
         y        = "",
         title    = str_glue("Empirical probability density function: daily change MRE COP/USD
                             Excluding observations with daily change equal to zero"), 
         subtitle = str_glue("Bins: {bins},
                             Observations: {length(cop_usd_trm_filter$trm_change[!is.na(cop_usd_trm_filter$trm_change)])}"),
         caption  = str_glue("Data source: Banco de la República (Colombia) & Superintendencia Financiera de Colombia (SFC) 
                             Last update: {cop_usd_trm$date[length(cop_usd_trm$date)]}")) +
    annotate(geom  = "label", 
             x     = 140.02, 
             y     = 0.06,
             label = str_glue("Mean: {mean(cop_usd_trm_filter$trm_change) %>% round(digits = 2)}
                              Median: {median(cop_usd_trm_filter$trm_change) %>% round(digits = 2)}
                              Standard deviation: {sd(cop_usd_trm_filter$trm_change) %>% round(digits = 2)}
                              Coefficient of variation: {(sd(cop_usd_trm_filter$trm_change) / mean(cop_usd_trm_filter$trm_change)) %>% round(digits = 2)}
                              Skewness: {skewness(cop_usd_trm_filter$trm_change) %>% round(digits = 2)}
                              Kurtosis: {kurtosis(cop_usd_trm_filter$trm_change) %>% round(digits = 2)}"),
             color = "white",
             fill  = palette_light()[[1]]) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          axis.text.x       = element_text(face = "bold", angle = 90, vjust = 0.5),
          axis.text.y       = element_text(face = "bold"))
```

# Simple model of exchange rate determination

- Decision of an individual between a national and a foreign financial instrument with a low risk

    + Assume you have $100$ COP in $t$ 
    
        + __Option 1__: Invest in a national financial instrument with and interest rate $i_t$ in COP
        
        + __Option 2__: Invest in a foreign financial instrument with and interest rate $i_t^*$ in USD
        
# Simple model of exchange rate determination

- Decision of individuals between a national and a foreign financial instrument with a low risk

    + Yield obtained in $t + 1$:

        + __Option 1__: $$(1 + i_t) \times 100$$

        + __Option 2__: $$\begin{split}
                           100 & \rightarrow \frac{100}{E_t} \\
                           & \rightarrow (1 + i_t^*) \times \frac{100}{E_t} \\
                           & \rightarrow (1 + i_t^*) \times \frac{100}{E_t} \times E_{t + 1} \\
                           & \rightarrow (1 + i_t^*) \times 100 \times \frac{E_{t + 1}}{E_t} 
                           \end{split}$$
                      
# Simple model of exchange rate determination

- Decision of an individual between a national and a foreign financial instrument with a low risk

    + $(1 + i_t) \times 100 > (1 + i_t^*) \times 100 \times \frac{E_{t + 1}}{E_t}$ individuals will have only national financial instruments
    
    + $(1 + i_t) \times 100 < (1 + i_t^*) \times 100 \times \frac{E_{t + 1}}{E_t}$ individuals will have only foreign financial instruments
    
    + $(1 + i_t) \times 100 = (1 + i_t^*) \times 100 \times \frac{E_{t + 1}}{E_t}$ individuals will have national and foreign financial instruments
    
        + In an economy individuals have national and foreign financial instruments. Therefore in the long run we have that $(1 + i_t) \times 100 = (1 + i_t^*) \times 100 \times \frac{E_{t + 1}}{E_t}$
        
# Simple model of exchange rate determination

- Decision of an individual between a national and a foreign financial instrument with a low risk

$$\begin{split}
   (1 + i_t) \times 100 & = (1 + i_t^*) \times 100 \times \frac{E_{t + 1}}{E_t} \\
   (1 + i_t) & = (1 + i_t^*) \times \frac{E_{t + 1}}{E_t} \\
   \frac{(1 + i_t)}{(1 + i_t^*)} \times E_t & = E_{t + 1} \\
   E_{t + 1} & = \frac{(1 + i_t)}{(1 + i_t^*)} \times E_t
   \end{split}$$

- We can forecast the exchange rate in $t + 1$, $E_{t + 1}$, using information in $t$, $i_t, i_t^*, E_t$  

# Simple model of exchange rate determination

- Using $E_{t + 1} = \frac{(1 + i_t)}{(1 + i_t^*)} \times E_t$ to forecast $E_{t + 1}$ 3 months ahead

    + Data

        + 3-month or 90-day rates and yields: Certificates of deposit for Colombia (COLIR3TCD01STM)[^3]

        + 3-Month or 90-day Rates and Yields: Certificates of Deposit for the United States (IR3TCD01USM156N)[^4]

        + Monthly mean Market Representative Exchange Rate (MRE)

    + $t + 1$

        + 3 months later
        
[^3]: FRED Economic Data | St. Louis FED: https://fred.stlouisfed.org/
[^4]: FRED Economic Data | St. Louis FED: https://fred.stlouisfed.org/

# Simple model of exchange rate determination

- Using $E_{t + 1} = \frac{(1 + i_t)}{(1 + i_t^*)} \times E_t$ to forecast $E_{t + 1}$ 3 months ahead

```{r, out.width="80%"}

# Calculate montly mean trm to convert data into monthly
cop_usd_trm_mean_month <- cop_usd_trm %>%
  filter_by_time(.date_var   = date, 
                 .start_date = "1991-12-01", 
                 .end_date   = floor_date(max(cop_usd_trm$date), unit = "month") %-time% "1 day") %>% 
  summarize_by_time(.date_var = date, 
                    .by       = "month", 
                    value     = mean(trm)) %>%
  set_names(nm = c("date", "trm_mean_month"))

# Information about interest rates in COL and USA
i_col_usa <- tq_get(x    = c("COLIR3TCD01STM", "IR3TCD01USM156N"), 
       get  = "economic.data",
       # There is missing data in 2020-04-01 for USA (IR3TCD01USM156N)
       from = "1991-12-01") %>%
  pivot_wider(id_cols = date, 
              names_from  = symbol,
              values_from = price) %>%
  set_names(nm = c("date", "i_col", "i_usa"))

# Joining data about trm COP/USA and interest rates in COL and USA 
i_col_usa_trm <- i_col_usa %>%
  left_join(y  = cop_usd_trm_mean_month,
            by = "date") %>%
  # Expressing interest rates without percent
  mutate(i_col = i_col / 100,
         i_usa = i_usa / 100)


# Comparing forecasts with actual values
i_col_usa_trm_forecast <- i_col_usa_trm %>%
  mutate(trm_forecast_3_month = ((1 + i_col) / (1 + i_usa)) * trm_mean_month) %>%
  select(date, trm_forecast_3_month) %>%
  mutate(date = date %m+% period("3 months")) %>%
  left_join(i_col_usa_trm, by = "date") %>% 
  select(date, trm_mean_month, trm_forecast_3_month) %>% 
  # Dropping forecasts because I don't nothing to compare with
  drop_na() %>% 
  mutate(error = abs(trm_mean_month - trm_forecast_3_month))

# Plot

# Data
clean_data <- i_col_usa_trm_forecast %>%
  select(date, trm_mean_month, trm_forecast_3_month) %>% 
  pivot_longer(cols = trm_mean_month:trm_forecast_3_month) %>% 
  mutate(name = case_when(
    name == "trm_mean_month"       ~ "Actual value",
    name == "trm_forecast_3_month" ~ "Forecast",
    TRUE ~ name),
    date = ceiling_date(date, unit = "month") %-time% "1 day")

# Clean plot
clean_data %>% 
  ggplot() +
  geom_line(aes(x     = date,
                y     = value,
                group = name,
                color = name)) +
  scale_color_tq() +
  labs(x        = "",
       y        = "COP/USD",
       color    = "",
       title    = "Forecasting Monthly mean Market Representative Exchange Rate (MRE)",
       subtitle = str_glue("Period: {clean_data$date[1]} - {clean_data$date[length(clean_data$date)]},
                             Observations: {length(clean_data$date) / 2}")) +
  theme(panel.border      = element_rect(fill = NA, color = "black"),
        plot.background   = element_rect(fill = "#f3fcfc"),
        panel.background  = element_rect(fill = "#f3f7fc"),
        legend.background = element_rect(fill = "#f3fcfc"),
        plot.title        = element_text(face = "bold"),
        axis.title        = element_text(face = "bold"),
        legend.title      = element_text(face = "bold"),
        legend.position   = "bottom",
        axis.text         = element_text(face = "bold"))
```

# Simple model of exchange rate determination

- Forecast error: $|\text{Actual value - Forecast}|$

```{r, out.width="80%"}

i_col_usa_trm_forecast %>% 
    ggplot() + 
    geom_histogram(aes(x = error, y = after_stat(density)),
                   bins = bins + 1, 
                   color = "black", 
                   fill  = palette_light()[[1]],
                   alpha = 0.8, 
                   boundary = min(i_col_usa_trm_forecast$error)) +
    geom_density(aes(x = error), 
                 color    = palette_light()[[2]],
                 size     = 0.5,
                 linetype = "longdash") +
    scale_x_continuous(labels = scales::number_format(accuracy = 0.01),
                       breaks = seq(from = min(i_col_usa_trm_forecast$error),
                                    to   = max(i_col_usa_trm_forecast$error), 
                                    by = (max(i_col_usa_trm_forecast$error) - min(i_col_usa_trm_forecast$error)) / bins)) +
    geom_vline(xintercept = mean(i_col_usa_trm_forecast$error),
               color      = palette_light()[[3]],
               size       = 1) +
    geom_segment(data = tibble(x    = (mean(i_col_usa_trm_forecast$error) - sd(i_col_usa_trm_forecast$error)),
                               y    = 0,
                               xend = (mean(i_col_usa_trm_forecast$error) + sd(i_col_usa_trm_forecast$error)),
                               yend = 0),
                 aes(x = x, y = y, xend = xend, yend = yend),
                 color   = palette_light()[[10]],
                 size    = 1) +
    labs(x        = "",
         y        = "",
         title    = "Frequency distribution: forecasting error", 
         subtitle = str_glue("Period: {i_col_usa_trm_forecast$date[1]} - {i_col_usa_trm_forecast$date[length(i_col_usa_trm_forecast$date)]},
                             Observations: {length(i_col_usa_trm_forecast$date)}
                             Bins: {bins}")) +
    annotate(geom  = "label",
             x     = 450,
             y     = 0.003,
             label = str_glue("Mean: {mean(i_col_usa_trm_forecast$error) %>% round(digits = 2)}
                              Median: {median(i_col_usa_trm_forecast$error) %>% round(digits = 2)}
                              Standard deviation: {sd(i_col_usa_trm_forecast$error) %>% round(digits = 2)}
                              Coefficient of variation: {(sd(i_col_usa_trm_forecast$error) / mean(i_col_usa_trm_forecast$error)) %>% round(digits = 2)}
                              Skewness: {skewness(i_col_usa_trm_forecast$error) %>% round(digits = 2)}
                              Kurtosis: {kurtosis(i_col_usa_trm_forecast$error) %>% round(digits = 2)}"),
             color = "white",
             fill  = palette_light()[[1]]) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          axis.text.x       = element_text(face = "bold", angle = 90, vjust = 0.5),
          axis.text.y       = element_text(face = "bold"))
```

# Implicit devaluation

- A possible way to calculate the implicit devaluation:

$$\begin{split}
   \text{Implicit devaluation} & = E_{t + 1} - E_t \\
   & = \frac{(1 + i_t)}{(1 + i_t^*)} \times E_t - E_t \\
   & = \bigg[ \frac{(1 + i_t)}{(1 + i_t^*)} - 1 \bigg] \times E_t \\
   & = \bigg[ \frac{i_t - i_t^*}{1 + i_t^*} \bigg] \times E_t
   \end{split}$$

# Acknowledgments

- To my family that supports me

- To the taxpayers of Colombia and the __[UMNG students](https://www.umng.edu.co/estudiante)__ who pay my salary

- To the __[Business Science](https://www.business-science.io/)__ and __[R4DS Online Learning](https://www.rfordatasci.com/)__ communities where I learn __[R](https://www.r-project.org/about.html)__ 

- To the __[R Core Team](https://www.r-project.org/contributors.html)__, the creators of __[RStudio IDE](https://rstudio.com/products/rstudio/)__ and the authors and maintainers of the packages __[tidyverse](https://CRAN.R-project.org/package=tidyverse)__, __[lubridate](https://CRAN.R-project.org/package=lubridate)__, __[tidyquant](https://CRAN.R-project.org/package=tidyquant)__, __[moments](https://CRAN.R-project.org/package=moments)__, __[timetk](https://CRAN.R-project.org/package=timetk)__ and __[tinytex](https://CRAN.R-project.org/package=tinytex)__ for allowing me to access these tools without paying for a license

- To the __[Linux kernel community](https://www.kernel.org/category/about.html)__ for allowing me the possibility to use some __[Linux distributions](https://static.lwn.net/Distributions/)__ as my main __[OS](https://en.wikipedia.org/wiki/Operating_system)__ without paying for a license

# References