---
title: "Selecting and managing entry modes"
author: "Luis Francisco Gomez Lopez"
date: 2022-06-10 10:58:30
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme: structurebold
    theme: AnnArbor
    fig_caption: true
  slidy_presentation: default
bibliography: econ_glob_faedis.bib
link-citations: yes
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{fontawesome5}
  - \usepackage{xcolor}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo      = FALSE, 
                      warning   = FALSE, 
                      message   = FALSE,
                      fig.align = "center")
```

```{r libraries}

library(DiagrammeR)
library(comtradr)
library(tidyverse)
library(countrycode)
library(treemapify)
library(tidyquant)
library(fs)
library(knitr)
library(kableExtra)
```

# Contents

- Please Read Me
- Purpose
- Entry modes for international markets
- Exporting goods in Colombia
- Importing goods in Colombia
- Franchising in Colombia
- Turnkey project and Joint venture: cement plant Río Claro (Sonsón, Colombia) case study 
- Acknowledgments
- References

# Please Read Me

- Check the message __Welcome greeting__ published in the News Bulletin Board.

- Dear student please edit your profile uploading a photo where your face is clearly visible.

- The purpose of the virtual meetings is to answer questions and not to make a summary of the study material.

- This presentation is based on [@wild_international_2020, Chapter 13]

# Purpose

Introduce the students to the different entry modes companies use to do international business and participate directly into the international markets

# Entry modes for international markets

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
  
  'Entry\nmodes';

  node [shape = oval, color = '#E31A1C']

  'Trade';
  
  node [shape = oval, color = '#18BC9C']
  
  'Exporting';
  'Importing';
  'Countertrade';
  
  node [shape = oval, color = '#CCBE93']
  
  'Direct';
  'Indirect';
  'Barter';
  'Counterpurchase';
  'Offset';
  'Switching trading';
  'Buyback';
  
  node [shape = oval, color = '#A6CEE3']
  
  'Sales\nrepresentative';
  'Distributor';
  
  'Agent';
  'Export management\ncompany';
  'Export trading\ncompany';
  
  node [shape = oval, color = '#CCBE93']
  
  'Direct';
  
  'Entry\nmodes'-> 'Trade' ;
  
  'Trade' -> 'Exporting';
  'Trade' -> 'Importing';
  'Trade' -> 'Countertrade';
  
  'Exporting' -> 'Direct';
  'Exporting' -> 'Indirect';
  'Countertrade'-> 'Barter';
  'Countertrade'-> 'Counterpurchase';
  'Countertrade'-> 'Offset';
  'Countertrade'-> 'Switching trading';
  'Countertrade'-> 'Buyback';
  
  'Direct' -> 'Sales\nrepresentative';
  'Direct' -> 'Distributor';
  'Indirect'-> 'Agent';
  'Indirect'-> 'Export management\ncompany';
  'Indirect'-> 'Export trading\ncompany';
  
}
")
```

# Entry modes for international markets

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
  'Entry\nmodes';

  node [shape = oval, color = '#E31A1C']

  'Contractual';
  'Investment';
  
  node [shape = oval, color = '#18BC9C']
  
  'Licensing';
  'Franchising';
  'Management contracts';
  'Turnkey project';
  'Wholly owned subsidiary';
  'Joint venture';
  'Strategic alliance';
  
  node [shape = oval, color = '#CCBE93']
  
  'Forward Integration';
  'Backward Integration';
  'Buyback';
  'Multistage';

  'Entry\nmodes'-> 'Contractual';
  'Entry\nmodes'-> 'Investment';
  
  'Contractual' -> 'Licensing';
  'Contractual' -> 'Franchising';
  'Contractual' -> 'Management contracts';
  'Contractual' -> 'Turnkey project';
  'Investment' -> 'Wholly owned subsidiary';
  'Investment' -> 'Joint venture';
  'Investment' -> 'Strategic alliance';
  
  'Joint venture' -> 'Forward Integration';
  'Joint venture' -> 'Backward Integration';
  'Joint venture' -> 'Buyback';
  'Joint venture' -> 'Multistage';
  
}
")
```

# Exporting goods in Colombia

```{r, out.width="90%"}

# Data
col_2021_exports <- comtradr::ct_search(reporters = "Colombia",
          partners = "All",
          trade_direction = "exports",
          freq = "annual",
          start_date = 2021,
          end_date = 2021,
          commod_codes = "TOTAL",
          type = "goods")

# Data clean
col_2021_exports_clean <- col_2021_exports %>%
    as_tibble() %>%
    select(year, trade_flow,
           reporter_iso, reporter,
           partner_iso, partner,
           commodity_code, commodity,
           trade_value_usd) %>%
    arrange(desc(trade_value_usd)) %>%
    # Areas excluded: "World", "Other Asia, nes", "Free Zones", "Areas, nes"
    filter(!(partner %in% c("World", "Other Asia, nes", "Free Zones", "Areas, nes", "Br. Indian Ocean Terr."))) %>%
    # Adding continent
    left_join(countrycode::codelist %>%
                  select(continent, country.name.en, iso3c), by = c("partner_iso" = "iso3c")) %>%
    select(year, trade_flow, reporter, partner_iso, partner, trade_value_usd, continent) %>%
    mutate(label_text = str_glue("{partner}
                                 {(trade_value_usd / sum(trade_value_usd)) %>% scales::percent(accuracy = 0.01)}"))

# Plot
col_2021_exports_clean %>%
    ggplot(aes(area  = trade_value_usd,
               label = label_text,
               subgroup = continent)) +
    geom_treemap(aes(fill = continent),
                 color = "black",
                 alpha = 0.8) +
    geom_treemap_text() +
    scale_fill_tq() +
    labs(x        = "",
         y        = "",
         fill     = "",
         title    = "Colombia goods exports by destination as percent of total exports: year 2021",
         subtitle = str_glue("Territories excluded: Free zones, British Indian Ocean Territory, Areas not elsewhere specified
                             and other Asia areas not elsewhere specified,
                             Products excluded: exports of services are not included"),
         caption  = str_glue("Source: United Nations International Trade Statistics Database (UN Comtrade),
                              Last update: 2022-06-10")) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          legend.position   = "bottom")
```

# Exporting goods in Colombia[^1]

```{r}

# Files
csv_files <- dir_ls(path = "007_export_col_monthly", regexp = "[.]csv$") 

# Data
export_col_comp_2021 <- csv_files %>%
  map_dfr(.f = read_csv, col_types = cols(POSAR = col_character(),
                                          NIT   = col_character(),
                                          FECH  = col_character())) %>%
  select(FECH, FOBDOL, NIT, RAZ_SIAL) 

# Unique names export
unique_name_export <- export_col_comp_2021 %>%
  select(NIT, RAZ_SIAL) %>%
  distinct(NIT, .keep_all = TRUE)

export_col_comp_2021 %>%
  group_by(NIT) %>%
  summarise(export_fob_us = sum(FOBDOL)) %>%
  ungroup() %>%
  arrange(desc(export_fob_us)) %>%
  left_join(unique_name_export, by = "NIT") %>%
  select(NIT, RAZ_SIAL, export_fob_us) %>%
  set_names(nm = c("NIT", "Name", "Exports (US dollars)")) %>%
  slice(1:10) %>%
  mutate(`Exports (US dollars)` = scales::dollar(`Exports (US dollars)`),
         NIT                    = str_remove(string = NIT, pattern = "^0+")) %>%
  kable(format = "latex", booktabs = TRUE, caption = "Top 10 companies according to exports (FOB) in 2021") %>%
  kable_styling(font_size = 6, latex_options = "striped") %>%
  row_spec(row = 0, bold = TRUE)
```

[^1]: Check out the full data set in https://sitios.dane.gov.co/anda-index/ > Economía > Comercio internacional > Estadísticas de exportaciones > Estadísticas de Exportaciones - EXPO - 2011 A 2021 > Expo_2021

# Importing goods in Colombia

```{r, out.width="90%"}

# Data
col_2021_imports <- ct_search(reporters = "Colombia",
                              partners = "All",
                              trade_direction = "imports",
                              freq = "annual",
                              start_date = 2021,
                              end_date = 2021,
                              commod_codes = "TOTAL",
                              type = "goods")

# Data clean
col_2021_imports_clean <- col_2021_imports %>%
    as_tibble() %>%
    select(year, trade_flow,
           reporter_iso, reporter,
           partner_iso, partner,
           commodity_code, commodity,
           trade_value_usd)  %>%
    arrange(desc(trade_value_usd)) %>%
    # Areas excluded: "World", "Other Asia, nes", "Free Zones", "Areas, nes"
    filter(!(partner %in% c("World", "Other Asia, nes", "Free Zones", "Colombia",
                            "Br. Indian Ocean Terr.", "Fr. South Antarctic Terr."))) %>%
    # Adding continent
    left_join(codelist %>%
                  select(continent, country.name.en, iso3c), by = c("partner_iso" = "iso3c")) %>%
    select(year, trade_flow, reporter, partner_iso, partner, trade_value_usd, continent) %>%
    mutate(label_text = str_glue("{partner}
                                 {(trade_value_usd / sum(trade_value_usd)) %>% scales::percent(accuracy = 0.01)}"))

# Plot
col_2021_imports_clean %>%
    # Drop NA values. See continent variable.
    drop_na() %>% 
    ggplot(aes(area  = trade_value_usd,
               label = label_text,
               subgroup = continent)) +
    geom_treemap(aes(fill = continent),
                 color = "black",
                 alpha = 0.8) +
    geom_treemap_text() +
    scale_fill_tq() +
    labs(x        = "",
         y        = "",
         fill     = "",
         title    = "Colombia goods imports by origin as percent of total exports: year 2021",
         subtitle = str_glue("Territories excluded: Free zones, British Indian Ocean Territory, Colombia
                             other Asia areas not elsewhere specified and French Southern and Antarctic Lands
                             Products excluded: exports of services are not included"),
         caption  = str_glue("Source: United Nations International Trade Statistics Database (UN Comtrade),
                              Last update: 2022-10-06")) +
    theme(panel.border      = element_rect(fill = NA, color = "black"),
          plot.background   = element_rect(fill = "#f3fcfc"),
          panel.background  = element_rect(fill = "#f3f7fc"),
          legend.background = element_rect(fill = "#f3fcfc"),
          plot.title        = element_text(face = "bold"),
          axis.title        = element_text(face = "bold"),
          legend.title      = element_text(face = "bold"),
          legend.position   = "bottom")
```

# Importing goods in Colombia[^2]

```{r}

# Files
csv_files <- dir_ls(path = "007_import_col_monthly/Impo_2021/", regexp = "[.]csv$")

# Data
import_col_comp_2021 <- csv_files %>%
  map_dfr(.f = read_csv, col_types = cols(NABAN   = col_character(),
                                          NIT     = col_character(),
                                          FECH    = col_character(),
                                          PAISGEN = col_character(),
                                          PAISPRO = col_character(),
                                          PAISCOM = col_character(),
                                          BANDERA = col_character(),
                                          COPAEX  = col_character(),
                                          ACUERDO = col_character(),
                                          ACTECON = col_character(), 
                                          DEPIM   = col_character(),
                                          DEREL   = col_character())) %>%
  select(FECH, VACID, NIT, RZIMPO)

# Unique names
unique_name_import <- import_col_comp_2021 %>%
  select(NIT, RZIMPO) %>%
  distinct(NIT, .keep_all = TRUE)

# Table
import_col_comp_2021 %>%
  group_by(NIT) %>%
  summarise(import_cif_us = sum(VACID)) %>%
  ungroup() %>%
  arrange(desc(import_cif_us)) %>%
  left_join(unique_name_import, by = "NIT") %>%
  select(NIT, RZIMPO, import_cif_us) %>%
  set_names(nm = c("NIT", "Name", "Imports (US dollars)")) %>%
  slice(1:10) %>%
  mutate(`Imports (US dollars)` = scales::dollar(`Imports (US dollars)`),
         NIT                    = str_remove(string = NIT, pattern = "^0+")) %>%
  kable(format = "latex", booktabs = TRUE, caption = "Top 10 companies according to imports (CIF) in 2021") %>%
  kable_styling(font_size = 6, latex_options = "striped") %>%
  row_spec(row = 0, bold = TRUE)
```

[^2]: Check out the full data set in https://sitios.dane.gov.co/anda-index/ > Economía > Comercio internacional > Estadísticas de importaciones > Estadísticas de Importaciones - IMPO - 2012 A 2021 > Impo_2021

# Franchising in Colombia

- Not explicit regulated by any local law or Andean regulation [@reyes_primer_2016]

    + Colombian Civil Code, Article 1602: franchisor and franchisee are free to perform a franchising relationship
    + Franchisor should register her trademarks, logos and slogans in agreement with the Andean Decision 486 of 2000[^3]
    
- Colfranquicias - Camara Colombiana de Franquicias: https://www.colfranquicias.com/

    + Franchises
    + Consultants
    + Suppliers
    
[^3]: It regulates the Common Regime on Industrial Property in Colombia

# Turnkey project and Joint venture: cement plant Río Claro (Sonsón, Colombia) case study 

- Construction of a cement plant in Sonsón, Colombia[^4]

    + Production capacity: 
    
        + 3150 tons per day of clinker
        + 1.35 million tons of cement per year
        
    + Cost
    
        + 238  million USD (224.6 million EUR)
        
    + Creation of Jobs
    
        + 800 jobs in the course of its construction
        + 220 direct and 250 indirect jobs when it becomes fully operational
        
[^4]: [@rowland_ecocementos_2017]
        
# Turnkey project and Joint venture: cement plant Río Claro (Sonsón, Colombia) case study

- Commissioned by Ecocementos S.A.S

    + Joint venture between Corona (Colombia) and Cementos Molins (Spain)
    
- Construction company 

    + OHL Industrial (Spain)

- Equipment supplier company

    + FLSmidth (Denmark)
    
# Acknowledgments

- To my family that supports me

- To the taxpayers of Colombia and the __[UMNG students](https://www.umng.edu.co/estudiante)__ who pay my salary

- To the __[Business Science](https://www.business-science.io/)__ and __[R4DS Online Learning](https://www.rfordatasci.com/)__ communities where I learn __[R](https://www.r-project.org/about.html)__ 

- To the __[R Core Team](https://www.r-project.org/contributors.html)__, the creators of __[RStudio IDE](https://rstudio.com/products/rstudio/)__ and the authors and maintainers of the packages __[tidyverse](https://CRAN.R-project.org/package=tidyverse)__, __[knitr](https://CRAN.R-project.org/package=knitr)__, __[kableExtra](https://CRAN.R-project.org/package=kableExtra)__, __[tidyquant](https://CRAN.R-project.org/package=tidyquant)__, __[comtradr](https://CRAN.R-project.org/package=comtradr)__, __[countrycode](https://CRAN.R-project.org/package=countrycode)__,
__[treemapify](https://CRAN.R-project.org/package=treemapify)__,
__[fs](https://CRAN.R-project.org/package=fs)__,
__[DiagrammeR](https://CRAN.R-project.org/package=DiagrammeR)__ and __[tinytex](https://CRAN.R-project.org/package=tinytex)__ for allowing me to access these tools without paying for a license

- To the __[Linux kernel community](https://www.kernel.org/category/about.html)__ for allowing me the possibility to use some __[Linux distributions](https://static.lwn.net/Distributions/)__ as my main __[OS](https://en.wikipedia.org/wiki/Operating_system)__ without paying for a license

# References
