---
title: "Managing international operations"
author: "Luis Francisco Gomez Lopez"
date: 2020-09-07
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme: structurebold
    theme: AnnArbor
    fig_caption: true
  slidy_presentation: default
bibliography: econ_glob_faedis.bib
link-citations: yes
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{fontawesome5}
  - \usepackage{xcolor}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo      = FALSE, 
                      warning   = FALSE, 
                      message   = FALSE,
                      fig.align = "center")
```

```{r libraries}

library(DiagrammeR)
```

# Contents

- Please Read Me
- Purpose
- Production strategy
- Acquiring physical resources
- Key production concerns
- Financing business operations
- Acknowledgments
- References

# Please Read Me

- Check the message __Welcome greeting__ published in the News Bulletin Board.

- Dear student please edit your profile uploading a photo where your face is clearly visible.

- The purpose of the virtual meetings is to answer questions and not to make a summary of the study material.

- This presentation is based on [@wildInternationalBusinessChallenges2020, Chapter 15]

# Purpose

Understand the elements to consider when formulating production strategies and the issues when acquiring physical resources

# Production strategy

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
 
  'Production\nstrategy';

  node [shape = oval, color = '#E31A1C']

  'Capacity\nplanning';
  'Facilities\nlocation\nplanning';
  'Process\nplanning';
  'Facilities\nlayout\nplanning';
  
  node [shape = oval, color = '#18BC9C']
  
  'Location\neconomies';
  'Centralization\nvs\ndecentralization';
  'Standarization\nvs\nadaptation';
  
  'Production\nstrategy' -> 'Capacity\nplanning';
  'Production\nstrategy' -> 'Facilities\nlocation\nplanning';
  'Production\nstrategy' -> 'Process\nplanning';
  'Production\nstrategy' -> 'Facilities\nlayout\nplanning';
  
  'Capacity\nplanning' -> 'Location\neconomies';
  'Capacity\nplanning' -> 'Centralization\nvs\ndecentralization';
  
  'Process\nplanning' -> 'Standarization\nvs\nadaptation';
  
}
")
```

# Production strategy

- Capacity planning

    + Ability to produce enough output to satisfy market demand [@wildInternationalBusinessChallenges2020, Chapter 15, p 388]  

- Facilities location planning

    + Selecting the location for production facilities [@wildInternationalBusinessChallenges2020, Chapter 15, p 388]

- Process planning

    + Deciding the process that the company will be use to create its product [@wildInternationalBusinessChallenges2020, Chapter 15, p 390]
    
- Facilities layout planning

    + Deciding the spatial arrangement of production processes within production facilities [@wildInternationalBusinessChallenges2020, Chapter 15, p 391]

# Acquiring physical resources

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
 
  'Acquiring\nphysical\nresources';

  node [shape = oval, color = '#E31A1C']

  'Make\ndecision';
  'Buy\ndecision';
  'Raw\nmaterials';
  'Fixed\nassets';
  
  node [shape = oval, color = '#18BC9C']
  
  'Vertical\nintegration';
  'Outsourcing';
  
  node [shape = oval, color = '#CCBE93']
  
  'Lower\ncosts';
  'Greater\ncontrol';
  'Lower\nrisk';
  'Greater\nflexibility';
  'Market\npower';
  
  'Acquiring\nphysical\nresources' -> 'Make\ndecision';
  'Acquiring\nphysical\nresources' -> 'Buy\ndecision';
  'Acquiring\nphysical\nresources' -> 'Raw\nmaterials';
  'Acquiring\nphysical\nresources' -> 'Fixed\nassets';
  
  'Make\ndecision' -> 'Vertical\nintegration';
  'Buy\ndecision' -> 'Outsourcing';
  
  'Vertical\nintegration' -> 'Lower\ncosts';
  'Vertical\nintegration' -> 'Greater\ncontrol';
  'Outsourcing' -> 'Lower\nrisk';
  'Outsourcing' -> 'Greater\nflexibility';
  'Outsourcing' -> 'Market\npower';
  
}
")
```

# Acquiring physical resources

- Vertical integration

    + Extension of company activities into stages in production that provide a company's inputs or absorb its output [@wildInternationalBusinessChallenges2020, Chapter 15, p 392]
    
        + Backward integration
        + Forward integration
        
- Outsourcing

    + The practice of buying from another company a product that is part of a company's value-added activities [@wildInternationalBusinessChallenges2020, Chapter 15, p 393]

# Key production concerns

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
 
  'Key\nproduction\nconcerns';

  node [shape = oval, color = '#E31A1C']

  'Quality\nimprovement\nefforts';
  'Shipping\nand\\ninventory costs';
  'Reinvestment\nvs\ndivestment';
  
  node [shape = oval, color = '#18BC9C']
 
  'Total quality\nmanagement (TQM)';
  'ISO 9000';
  'Just-in-time (JIT)\nmanufacturing';
  
  'Key\nproduction\nconcerns' -> 'Quality\nimprovement\nefforts';
  'Key\nproduction\nconcerns' -> 'Shipping\nand\\ninventory costs';
  'Key\nproduction\nconcerns' -> 'Reinvestment\nvs\ndivestment';

  'Quality\nimprovement\nefforts' -> 'Total quality\nmanagement (TQM)';
  'Quality\nimprovement\nefforts' -> 'ISO 9000';
  'Shipping\nand\\ninventory costs' -> 'Just-in-time (JIT)\nmanufacturing';
  
}
")
```

# Key production concerns

- Quality improvement efforts [@wildInternationalBusinessChallenges2020, Chapter 15, p 395]

    + Keep low production costs
    
        + Reduce waste in valuable inputs
        + Reduce costs of retrieving defective products
        + Reduce disposal costs that result from defective products
        
    + Create costumer value

- Shipping and inventory costs

    + Just-in-time (JIT) manufacturing
    
        + Inventory is kept to a minimum and inputs arrive when they are needed
        
- Reinvesting and divesting

    + Reinvestment: increasing some type of asset by a company  
    + Divestment: reductioning some type of asset by a company

# Financing business operations

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
 
  'Financing\nbusiness\noperations';

  node [shape = oval, color = '#E31A1C']

  'Borrowing';
  'Issuing\nequity';
  'Internal\nfunding';
  
  'Financing\nbusiness\noperations' -> 'Borrowing';
  'Financing\nbusiness\noperations' -> 'Issuing\nequity';
  'Financing\nbusiness\noperations' -> 'Internal\nfunding';
  
}
")
```

# Financing business operations

- Borrowing

    + Debt

- Issuing equity

    + Stock ownership

- Internal funding

    + Resources from parent companies
    + Revenue from selling company products

# Acknowledgments

- To my family that supports me

- To the taxpayers of Colombia and the __[UMNG students](https://www.umng.edu.co/estudiante)__ who pay my salary

- To the __[Business Science](https://www.business-science.io/)__ and __[R4DS Online Learning](https://www.rfordatasci.com/)__ communities where I learn __[R](https://www.r-project.org/about.html)__ 

- To the __[R Core Team](https://www.r-project.org/contributors.html)__, the creators of __[RStudio IDE](https://rstudio.com/products/rstudio/)__ and the authors and maintainers of the packages __[DiagrammeR](https://CRAN.R-project.org/package=DiagrammeR)__ and __[tinytex](https://CRAN.R-project.org/package=tinytex)__ for allowing me to access these tools without paying for a license

- To the __[Linux kernel community](https://www.kernel.org/category/about.html)__ for allowing me the possibility to use some __[Linux distributions](https://static.lwn.net/Distributions/)__ as my main __[OS](https://en.wikipedia.org/wiki/Operating_system)__ without paying for a license

# References
