---
title: "Political economy and ethics"
author: "Luis Francisco Gomez Lopez"
date: 2022-10-06 11:02:14
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme: structurebold
    theme: AnnArbor
    fig_caption: true
  slidy_presentation: default
bibliography: econ_glob_faedis.bib
link-citations: yes
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{fontawesome5}
  - \usepackage{xcolor}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo      = FALSE, 
                      warning   = FALSE, 
                      message   = FALSE,
                      fig.align = "center")
```

```{r libraries}

library(tidyverse)
library(DiagrammeR)
library(tidyquant)
library(readxl)
```

# Contents

- Please Read Me
- Purpose
- Macroenvironment and the Company
- Political macroenvironment
- Legal macroenvironment
- Social responsibility: ISO 26000 (2010)
- Acknowledgments
- References

# Please Read Me

- Check the message __Welcome greeting__ published in the News Bulletin Board.

- Dear student please edit your profile uploading a photo where your face is clearly visible.

- The purpose of the virtual meetings is to answer questions and not to make a summary of the study material.

- This presentation is based on [@wild_international_2019, Chapter 3]

# Purpose

Examine the main types of political, economical and legal systems around the world and understand the importance of ethical behavior and social responsibility in a international context

#  Macroenvironment and the Company

- Set of external factors and forces that are not controlled by an organization but that influence its development.

```{r, out.width="75%"}

#Plot
ggplot(data = tibble(x = 0, y = 0)) + 
    ## Company
    annotate(geom = "text", 
             x        = 0, 
             y        = 0,
             label    = "Company",
             size     = 3,
             fontface = "bold") +
    geom_rect(aes(xmin = -0.4,
                  xmax =  0.4,
                  ymin = -0.4,
                  ymax =  0.4),
              alpha = 0.3,
              fill  = "red",
              color = "red") +
    ## Micro environment
    geom_rect(aes(xmin = -2,
                  xmax =  2,
                  ymin = -2,
                  ymax =  2),
              alpha = 0.25,
              color = "blue") +
    annotate(geom = "text", 
             x        = 0, 
             y        = 1,
             label    = str_glue("Micro environment"),
             size     = 6,
             fontface = "bold") +
    annotate(geom = "text", 
             x     = 0, 
             y     = -1.2,
             label = str_glue("Clients - Suppliers - Intermediaries - Competitors - General Public"),
             size  = 3.5) +
    ## Macro environment
    geom_rect(aes(xmin = -3,
                  xmax =  3,
                  ymin = -3,
                  ymax =  3),
              alpha = 0.1,
              color = "purple") +
    annotate(geom     = "text", 
             x        = 0, 
             y        = 2.5,
             label    = str_glue("Macro environment"),
             size     = 8,
             fontface = "bold") +
    annotate(geom = "text", 
             x     =  0, 
             y     = -2.5,
             label = str_glue("Economic - Political - Social - Technological - Ecological - Legal"),
             size  = 5) +
    theme_void() +
    labs(caption = "Based on https://foda-dafo.com/ ")
```

# Political macroenvironment

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = TB]

  node [shape = circle, color = '#2C3E50']
 
  'Political\nsystems';

  node [shape = oval, color = '#E31A1C']

  'Anarchism';
  'Totalitarism';
  'Pluralism';
  
  node [shape = oval, color = '#18BC9C']
  
  'Theocracy';
  'Secular';
  'Democracy';
  
  node [shape = oval, color = '#CCBE93']
  
  'Imposed\nauthority';
  'Lack\nof\nconstitutional\nguarantees';
  'Restricted\nparticipation';
  'Freedom\nof\nexpression';
  'Periodic\nelections';
  'Full\ncivil\nand\nproperty\nrights';
  'Minority\nrights';
  'Nonpolitical\nbureaucracies';
  
  'Political\nsystems'-> 'Anarchism';
  'Political\nsystems'-> 'Totalitarism';
  'Political\nsystems'-> 'Pluralism';
  
  'Totalitarism' -> 'Theocracy';
  'Totalitarism' -> 'Secular';
  'Pluralism' -> 'Democracy';
  
  'Theocracy' -> 'Imposed\nauthority';
  'Theocracy' -> 'Lack\nof\nconstitutional\nguarantees';
  'Theocracy' -> 'Restricted\nparticipation';
  'Secular' -> 'Imposed\nauthority';
  'Secular' -> 'Lack\nof\nconstitutional\nguarantees';
  'Secular' -> 'Restricted\nparticipation';
  'Democracy' -> 'Freedom\nof\nexpression';
  'Democracy' -> 'Periodic\nelections';
  'Democracy' -> 'Full\ncivil\nand\nproperty\nrights';
  'Democracy' -> 'Minority\nrights';
  'Democracy' -> 'Nonpolitical\nbureaucracies';
  
}
")
```

# Economic macroenvironment

```{r, out.width="60%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = TB]

  node [shape = circle, color = '#2C3E50']
 
  'Economic\nsystems';

  node [shape = oval, color = '#E31A1C']

  'Central\nplanned';
  'Market\neconomy';
  
  node [shape = oval, color = '#18BC9C']
  
  'Government\nrole';
  
  node [shape = oval, color = '#CCBE93']
  
  'Enforcing\nantitrust\nlaws';
  'Preserving\nproperty\nrights';
  'Stable\nfiscal\nand\nmonetary\nenvironment';
  'Political\nstability'

  'Economic\nsystems' -> 'Central\nplanned';
  'Economic\nsystems' -> 'Market\neconomy';
  
  'Market\neconomy' -> 'Government\nrole';
  
  'Government\nrole' -> 'Enforcing\nantitrust\nlaws';
  'Government\nrole' -> 'Preserving\nproperty\nrights';
  'Government\nrole' -> 'Stable\nfiscal\nand\nmonetary\nenvironment';
  'Government\nrole' -> 'Political\nstability'
  
}
")
```

# Legal macroenvironment

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = TB]

  node [shape = circle, color = '#2C3E50']
 
  'Legal\nsystems';
  'Legal\nissues'

  node [shape = oval, color = '#E31A1C']

  'Common law';
  'Civil law';
  'Theocratic law';
  'Intellectual\nproperty';
  'Product\nsafety\nand\nliability';
  'Taxation';
  'Antitrust\nregulations'
  
  node [shape = oval, color = '#18BC9C']
  
  'Tradition:\nA country’s\nlegal history';
  'Precedent:\nPast cases\nthat have come\nbefore the courts';
  'Usage:\nHow laws are\napplied in specific\nsituations';
  'Meet\nstandards';
  'Responsability\nfor\ndamage';
  
  'Legal\nsystems' -> 'Common law';
  'Legal\nsystems' -> 'Civil law';
  'Legal\nsystems' -> 'Theocratic law';
  'Legal\nissues' -> 'Intellectual\nproperty';
  'Legal\nissues' -> 'Product\nsafety\nand\nliability';
  'Legal\nissues' -> 'Taxation';
  'Legal\nissues' -> 'Antitrust\nregulations';
  
  'Common law' -> 'Tradition:\nA country’s\nlegal history';
  'Common law' -> 'Precedent:\nPast cases\nthat have come\nbefore the courts';
  'Common law' -> 'Usage:\nHow laws are\napplied in specific\nsituations';
  'Product\nsafety\nand\nliability' -> 'Meet\nstandards';
  'Product\nsafety\nand\nliability' -> 'Responsability\nfor\ndamage';
   
}
")
```

# Legal macroenvironment

- Tax complexity [@hoppe_tax_2021]

```{r, out.width="80%"}

# Data
# https://www.taxcomplexity.org/
tax_complex_ind_2020 <- read_excel(path      = "009_tax_complexity_2022-02-14.xlsx", 
                                   sheet     = 2, 
                                   range     = "A1:C228", 
                                   col_names = TRUE) %>% 
  set_names(nm = c("country", "year", "tax_complex_ind")) %>% 
  filter(year == 2020) %>% 
  arrange(desc(tax_complex_ind))


# Plot
tax_complex_ind_2020 %>% 
  ggplot() + 
  geom_col(aes(x       = fct_reorder(.f = country, .x = tax_complex_ind), 
               y       = tax_complex_ind,
               fill    = country == "Colombia"), 
           color       = "black",
           alpha       = 0.6,
           show.legend = FALSE) +
  labs(x        = "Countries",
       y        = "Tax complexity index",
       fill    = "",
       title    = "Tax complexity index by country",
       # In the case of tax_complex_ind_2016$country[2] 
       ## search for Colombia
       subtitle = str_glue("Year: 2020
                           Index interpretation: values range between zero (not complex) and one (extremely complex)
                           Number of countries: {nrow(tax_complex_ind_2020)}
                           Red color: {tax_complex_ind_2020$country[3]} ({tax_complex_ind_2020$tax_complex_ind[3] %>% round(digits = 3)})
                           Maximum value: {tax_complex_ind_2020$country[1]} ({tax_complex_ind_2020$tax_complex_ind[1] %>% round(digits = 3)})
                           Minimum value: {tax_complex_ind_2020$country[length(tax_complex_ind_2020$country)]} ({tax_complex_ind_2020$tax_complex_ind[length(tax_complex_ind_2020$country)] %>% round(digits = 3)})"),
       caption  = str_glue("Data source: www.taxcomplexity.org
                            Last update: 2022-02-14")) +
  scale_y_continuous(limits = c(0,1)) + 
  scale_fill_tq() +
  theme(panel.border      = element_rect(fill = NA, color = "black"),
        plot.background   = element_rect(fill = "#f3fcfc"),
        panel.background  = element_rect(fill = "#f3f7fc"),
        legend.background = element_rect(fill = "#f3fcfc"),
        plot.title        = element_text(face = "bold"),
        axis.title        = element_text(face = "bold"),
        legend.title      = element_text(face = "bold"),
        axis.text         = element_text(face = "bold"), 
        axis.text.x       = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

# Legal macroenvironment

- Tax environment attractiveness for corporations [@schanz_tax_2017]

```{r, out.width="80%"}

# Data
# https://www.tax-index.org/
year_chosen <- 2018

tax_attract_ind <- read_excel(path      = "009_tax_index_custom_2021-03-21.xlsx", 
           sheet     = 1, 
           range     = "A3:Z1203", 
           col_names = TRUE, 
           na        = c("", "-")) %>% 
  select(Country, Year, `Tax Attractiveness Index (20 Components)`) %>% 
  set_names(nm = c("country", "year", "tax_attract_ind")) %>% 
  drop_na() %>% 
  arrange(desc(tax_attract_ind)) %>% 
  filter(year == year_chosen)

tax_attract_ind_col <- tax_attract_ind %>% 
  filter(year == year_chosen, country == "Colombia")

# Plot
tax_attract_ind %>% 
  ggplot() + 
  geom_col(aes(x       = fct_reorder(.f = country, .x = tax_attract_ind), 
               y       = tax_attract_ind,
               fill    = country == "Colombia"), 
           color       = "black",
           alpha       = 0.6,
           show.legend = FALSE) +
  labs(x        = "Countries",
       y        = "Tax attractiveness index",
       fill    = "",
       title    = "Attractiveness of the tax environment for corporations by country",
       subtitle = str_glue("Year: {year_chosen}
                           Index interpretation: values range between zero (not attractive) and one (extremely attractive)
                           Number of countries: {nrow(tax_attract_ind)}
                           Red color: {tax_attract_ind_col$country} ({tax_attract_ind_col$tax_attract_ind %>% round(digits = 3)})
                           Maximum value: {tax_attract_ind$country[1]} ({tax_attract_ind$tax_attract_ind[1] %>% round(digits = 3)})
                           Minimum value: {tax_attract_ind$country[length(tax_attract_ind$country)]} ({tax_attract_ind$tax_attract_ind[length(tax_attract_ind$country)] %>% round(digits = 3)})"),
       caption  = str_glue("Data source: https://www.tax-index.org/
                            Last update: 2121-03-12")) +
  scale_y_continuous(limits = c(0,1)) + 
  scale_fill_tq() +
  theme(panel.border      = element_rect(fill = NA, color = "black"),
        plot.background   = element_rect(fill = "#f3fcfc"),
        panel.background  = element_rect(fill = "#f3f7fc"),
        legend.background = element_rect(fill = "#f3fcfc"),
        plot.title        = element_text(face = "bold"),
        axis.title        = element_text(face = "bold"),
        legend.title      = element_text(face = "bold"),
        axis.text         = element_text(face = "bold"), 
        axis.text.x       = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

# Social responsibility: ISO 26000 (2010)

- Definition of social responsibility [@iso_iso_2010, Section 2, Definition 2.18]

    + "Responsibility of an organization for the impacts of its decisions and activities on society and the environment through transparent and ethical behaviour that:

      + Contributes to sustainable development, including health and the welfare of society
      + Takes into account the expectations of stakeholders
      + Is in compliance with applicable law and consistent with international norms of behaviour
      + Is integrated throughout the organization and practised in its relationships[^1]"
      
[^1]: Refers to the activities or the organization within its sphere of influence

# Social responsibility: ISO 26000 (2010)

- Principles of social responsibility [@iso_iso_2010, Section 4]

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = TB]

  node [shape = circle, color = '#2C3E50']
 
  '7\nprinciples';

  node [shape = oval, color = '#E31A1C']

  'Accountability';
  'Transparency';
  'Ethical\nbehaviour';
  'Respect\nfor\nstakeholder\ninterests';
  'Respect\nfor\nthe\nrule\nof\nlaw';
  'Respect\nfor\ninternational\nnorms\nof\nbehaviour';
  'Respect\nfor\nhuman\nrights';
  
  node [shape = oval, color = '#18BC9C']
  
  'Scrutinity';
  'Duty\nto\nrespond\nto\nscrutiny';
  'Honesty';
  'Equity';
  'Integrity';

  '7\nprinciples' -> 'Accountability';
  '7\nprinciples' -> 'Transparency';
  '7\nprinciples' -> 'Ethical\nbehaviour';
  '7\nprinciples' -> 'Respect\nfor\nstakeholder\ninterests';
  '7\nprinciples' -> 'Respect\nfor\nthe\nrule\nof\nlaw';
  '7\nprinciples' -> 'Respect\nfor\ninternational\nnorms\nof\nbehaviour';
  '7\nprinciples' -> 'Respect\nfor\nhuman\nrights';
  
  'Accountability' -> 'Scrutinity';
  'Accountability' -> 'Duty\nto\nrespond\nto\nscrutiny';
  'Ethical\nbehaviour' -> 'Honesty';
  'Ethical\nbehaviour' -> 'Equity';
  'Ethical\nbehaviour' -> 'Integrity';

}
")
```

# Social responsibility: ISO 26000 (2010)

- The organization, stakeholders and society [@iso_iso_2010, Section 5, Fig 2]

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = LR]

  node [shape = circle, color = '#2C3E50']
 
  'Society\nand\nthe\nenvironment';
  
  node [shape = plaintext]
  
  'Expectations';
  'Impacts ';

  node [shape = circle, color = '#E31A1C']

  'Organization';
  
  node [shape = plaintext]
  
  'Interests';
  'Impacts';
  
  node [shape = circle, color = '#18BC9C']
  
  'Stakeholders'

  'Society\nand\nthe\nenvironment' -> 'Expectations' [color = '#A6CEE3'];
  'Society\nand\nthe\nenvironment' -> 'Impacts '  [dir = back, color = '#CCBE93'];
  
  'Expectations' -> 'Organization' [color = '#A6CEE3'];
  'Impacts ' -> 'Organization' [dir = back, color = '#CCBE93'];
  
  'Organization' -> 'Interests' [dir = back, color = '#CCBE93'];
  'Organization' -> 'Impacts' [color = '#A6CEE3'];
  
  'Interests' -> 'Stakeholders' [dir = back, color = '#CCBE93'];
  'Impacts' -> 'Stakeholders' [color = '#A6CEE3'];

}
")
```

# Social responsibility: ISO 26000 (2010)

- Core subjects [@iso_iso_2010, Section 6]

    + Each core subject has specific issues where you can find a detail description in [@iso_iso_2010, Section 6, p 19-68] 

```{r, out.width="100%"}

grViz("
digraph boxes_and_circles {

  graph [rankdir = R]

  node [shape = circle, color = '#2C3E50']
 
  'Core\nsubjects';
  
  node [shape = oval, color = '#E31A1C']
  
  'Organizational\ngovernance';
  'Human\nrights';
  'Labour\npractices';
  'The\nenvironment';
  'Fair\noperating\npractices';
  'Consumer\nissues';
  'Community\ninvolvement\nand\ndevelopment'

  'Core\nsubjects' -> 'Organizational\ngovernance';
  'Core\nsubjects' -> 'Human\nrights';
  'Core\nsubjects' -> 'Labour\npractices';
  'Core\nsubjects' -> 'The\nenvironment';
  'Core\nsubjects' -> 'Fair\noperating\npractices';
  'Core\nsubjects' -> 'Consumer\nissues';
  'Core\nsubjects' -> 'Community\ninvolvement\nand\ndevelopment'

}
")
```

# Acknowledgments

- To my family that supports me

- To the taxpayers of Colombia and the __[UMNG students](https://www.umng.edu.co/estudiante)__ who pay my salary

- To the __[Business Science](https://www.business-science.io/)__ and __[R4DS Online Learning](https://www.rfordatasci.com/)__ communities where I learn __[R](https://www.r-project.org/about.html)__ 

- To the __[R Core Team](https://www.r-project.org/contributors.html)__, the creators of __[RStudio IDE](https://rstudio.com/products/rstudio/)__ and the authors and maintainers of the packages __[DiagrammeR](https://CRAN.R-project.org/package=DiagrammeR)__, __[tidyverse](https://CRAN.R-project.org/package=tidyverse)__, __[tidyquant](https://CRAN.R-project.org/package=tidyquant)__, __[readxl](https://CRAN.R-project.org/package=readxl)__ and __[tinytex](https://CRAN.R-project.org/package=tinytex)__ for allowing me to access these tools without paying for a license

- To the __[Linux kernel community](https://www.kernel.org/category/about.html)__ for allowing me the possibility to use some __[Linux distributions](https://static.lwn.net/Distributions/)__ as my main __[OS](https://en.wikipedia.org/wiki/Operating_system)__ without paying for a license

# References
